Prototype city generation for mobility simulation in urban typologies: a generalized framework

### 2017-12-21 manuscript/manuscript.tex
od cost estimation method

@@

>>>>

\begin{table}[h!]
  \centering
  \begin{tabular}{l l l l l }
    City/Typology & Microdata & Aggregate data & Land use & Transit \\
  \end{tabular}
  \caption{Data availability for candidate cities}
  \label{tab:avail}
\end{table}

@@

\subsection{Estimation of origin-destination matrices}
There are three key

\begin{table}[h!]\small
  \centering
  \begin{tabular}{l l l } \toprule
    \textbf{Parameters}            & \textbf{Description}  & \textbf{Notes} \\ \midrule
    \texttt{distance}     & Zone-zone distance (km) & \\
    \texttt{car\_cost\_erp} & Road pricing cost (monetary units) &  \\
    \texttt{car\_ivt}     & Car in-vehicle time  (hours) & \\
    \texttt{pub\_ivt}     & Public transit in-vehicle time (hours) & \\
    \texttt{pub\_walkt}   & Public transit access-egress walking time (hours) & \\
    \texttt{pub\_wtt}     & Public transit waiting time (hours) & \\
    \texttt{pub\_cost}    & Public transit cost between zones (monetary units) & \\
    \texttt{avg\_transfer}& Average number of public transit transfers between zones & \\
    \texttt{pub\_out}     & Public transit out-of-vehicle travel time (hours) & Sum  \texttt{pub\_walkt} and  \texttt{pub\_wtt} \\ \bottomrule
  \end{tabular}
  \caption{Operating cost parameters (Skim matrix elements) in SimMobility}
  \label{tab:opcosts}
\end{table}

\subsubsection{Initial estimates}
\begin{enumerate}
\item The zone-zone distance can be readily estimated by averaging the shortest-path distances for all unique OD pairings within a pair of zones. Given $P_{n_O n_D}$ as the shortest path for a given node-node OD pair, $n_On_D$, between two zones $O$ and $D$, then we can write
  \begin{equation}
    d_{OD} = \frac{\sum_{n_On_D \in V(O) \times V(D)}|| P_{n_On_D}||}{|V(O) \times V(D)|}
  \end{equation}
\item The road pricing cost can be zero for now, but these will be relevant for congestion pricing scenarios. Thus,
  \begin{equation}
    C^{rp}_{OD} = 0
  \end{equation}
\item Car in-vehicle time $CIVT$ can be computed using free-flow speeds $FFS_e$ along each edge $e$ of the shortest-path ODs for each zone pair to travel times, which are then averaged to obtain the final estimate:
  \begin{align}
    CIVT(P) &= \sum_{e \in P} \fr{||e||}{FFS_e}\\
    CIVT_{OD} &= \frac{\sum_{n_On_D \in V(O) \times V(D)} CIVT(P_{n_On_D})}{|V(O) \times V(D)|}
  \end{align}
\item Public transit in-vehicle time $PIVT$ is estimated using the procedure outlined in (iii) applied to the public transit graph
\item  Public transit access-egress 
\end{enumerate}
